---
name: Zahid
surname: Asghar
position: "Professor "
address: "School of Economics, Quaid-i-Azam University, Islamabad"
www: 
DOB: 14-10-1969
profilepic: 
email: "zasghar@qau.edu.pk"
twitter: zahedasghar
github: Zahidasghar
linkedin: Zahid Asghar
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::hyndman
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# About me

  I am applied econometrician and statistician with special interests in development economics, making sense of data through Data visualization and  have conducted a large number of trainings on data analytics using Excel, STATA, R and EVIEWS. I have expertise in using R , STATA and Excel , and comfortable in using Datawrapper, Tableau, SPSS and EVIEWS for data anlysis. I am actively engaged in playing with data particularly _PovCalnetR_, _PDHS_, _PSLM_, _WDI using R_ among many other survey data sets. I have published in gender, food security and other socio-economic issues both in national and international peer reviewed journals. I am keen in having better awareness of development indicators in the society and to contribute to an evidence based decision making in socio-economic policy. I have strengths both in Statistics and Economics

# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "SSC/MATRIC","1983-1985", "Board of Intermediate and Secondary Education", "Rawalpindi",
  "HSSC","1985-1987", "Board of Intermediate and Secondary Education", "Lahore",
  "Bachelor of Sceince", "1987-1990", "University of the Punjab", "Lahore, Pakistan",
  "Master of Statistics", "1990-92", "Bahauddin Zakaraya University", "Multan, Pakistan",
  "PhD Economics", "2002-2007", "Pakistan Institute of Development Economics", "Islamabad, Pakistan"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```


# Employment

*Quaid-i-Azam University, Islamabad* 

  Professor  (School of Economics) \hfill 2018-to-date 
  
  Director  (School of Economics) \hfill Jan 2019- Jan 2022

  Registrar  \hfill 2020-2021 

  Associate Professor  \hfill 2015-2018 

  Assistant Professor  \hfill 2002-2011 

  Lecturer \hfill 1994-2000 

*State Bank of Pakistan*

Senior Faculty, National Institute of Banking and Finance \hfill 2011-2013 

*Sultan Qaboos University, Oman* 
 Visiting Consultant (2009-10)


## Research Projects and Data Consultancy Projects: 

	Data Analysis of Tax on Services Sector 2012-2022 of Punjab 
	
	Data Analyst for Earning Projection Survey of Free-Lancing jobs
	under IGNITE, Ministry of Finance 2021, Pakistan   
	
	Data consultant for Ignite: National Technology Fund, Ministry of
	Finance 2019-20 
	
	Assessing Data requirements for SDGs through key informant
	interviews and surveys in progress under NRPU of the HEC (Current)
	Data were extracted from PSLM and HIES from 1998-2015-16 Surveys 
	
	Member of the team as a data analyst for a research project for
	financing agriculturists through a third party instead of  Arhtis
	at NIBAF, State Bank of Pakistan 2011-13 
	
	Consultant for a project on Biases in Consumer Price Index (PIDE)
	2007

## Member of Professional/Statutory Bodies 

 +    Senate Member, Pakistan Institute of Development Economics 2008-2011 
 
 +    Member Research Advisory Council on ‘Research for Social 
  Transformation and Advancement’ (RASTA) under PSDP of the Ministry 
  of Planning, Development and Special Initiatives, the Government of
  Pakistan, 2020-21 to-date 
 +    Member Technical Committee Price Indices , Pakistan Bureau of 
  Statistics 2013 to-date 
  
 +    LEAD fellow Cohort-19  
  
 +    Member Technical Committee SDGs , Pakistan Bureau of Statistics 
  
 +    Member Technical National Account Committee, Pakistan Bureau of
  Statistics 
  
 +    Member, Board of Studies and Faculty at various academic institutions
  

## More than 40 peer reviewed jorunal articles (some are listed below) 
  +  Shabnam,N, Santeramo,F.,Asghar,Z and  Antonio,S  “The Impact Of Food
 	Price Crises On The Demand For Nutrients In Pakistan” 
 	*Journal of South Asian Development* 11 (3), 305-327  
 	
 	
  +  Noor, Amna & Asghar, Zahid & Sarwar, Haroon & Arfeen, Irfanullah.
  (2021). Role of the ICT in Women Empowerment and Achieving SDGs: A
  Case Study of Women Labor Force in Developing Countries.
  *ETIKONOMI*. 20. 339-348. 10.15408/etk.v20i2.22045. 
  
  
  +  A Noor, Z Asghar, MI Arfeen, "Role of the ICT in Women's Empowerment
  and Achieving SDGs 2030: A Case Study of Pakistan by using PDHS
  Data." *Journal of Managerial Sciences*, 2021 
  
  +  Muhammad Asif, Zawar Hussain, Zahid Asghar, Muhammad Irfan Hussain,
  Mariya Raftab, Said Farooq Shah, Akbar Ali Khan,A statistical
  evidence of power law distribution in the upper tail of world
  billionaires’ data 2010–20,*Physica A: Statistical  Mechanics and its Applications*, Volume 581, 2021  
 
  +  M Aslam, C Ley, Z Hussain, SF Shah, Z Asghar “A new generator for
  proposing flexible lifetime distributions and its properties”
 *PloS One* 15 (4), e0231908	2020 

  +  Khan, F., Asghar, Z., Tipu, M., Rehman, A., Khan, A., & Rehman, T.
  "Effect of displacement on Adherence to TB Treatment: An
  observational study in TB patients from Internally Displaced Persons
  of Pakistan". *Pakistan Journal of Medical Sciences*, 37(3),2021 
	
  +  Asghar, Zahid and Khaild, Mahmood, “Biases in Consumer Price Index
  Methodology in Pakistan: Suggestions for Improvements” *Pakistan Development Review* Vol.47(3) (2008) 267-285. 
 	
  +  Musarrat Ijaz, Zahid Asghar & Asma Gul (2019) Ensemble of penalized
  logistic models for classification of high-dimensional data,
 *Communications in Statistics - Simulation and Computation*,
 DOI: 10.1080/03610918.2019.1595647 
 	
  +  Shahzad,M. Riaz, M. and Asghar,Z “On The Evaluation Of Different
  Forecasters' Performance” 	*Communication in Statistics,Computation  	and Simulations*  (2018)
 	
## Trainings conducted as a Trainer: (35+ Trainings) 
 +    *Econometrics Using STATA Under TVET Support Program in Pakistan*, 2-13 March, 2015
 +    Applied Econometrics, NIBAF, State Bank of Pakistan 14-18 December, 2017, Islamabad 
 +    **Data Management and Analysis Using STATA**, _International Rescue Committee_, 25-27 April, 2017 Islamabad 

 +    Workshop conducted for Mid-Career Management Course on “Data
	Visualization” Information Services Academy, Islamabad, December,
	2020 
	
 +    Resource Person for  ‘Data Visualization and its importance for
	Journalists and media’, Information Services Academy, Islamabad, 
	3rd January, 2020 
	
 +    Resource Person for Workshop on Applied Economics Using Softwares, School of
	Economics, QAU, 22-26 July,2019

 +    Resource Person for Workshop on Analysing Data Using Stata, Pakistan Institute of     Development Economics, Islamabad, 5-February,2019 
 +    Data Visualization for Policy Making Using Excel for Faculty Development Program,
	HEC, 2-Sessions, 20th January,2019 
 +    Resource Person for Workshop on Applied Econometrics, School of Economics, QAU, 
	4-6 Jan,2019 
 +    National Invited Speaker for “ Making Sense of Data Through Visualization,
	University of Malakand, Nov-2018 
 +    National Invited Speaker for “Data Visualization”, Women University, Multan
	11-May, 2018 
 +    Data, Data Visualization, and Data Driven Decision Making for Faculty Development
 +    Program, HEC, 2-Sessions, 20th January,2017 
 +    Teaching Basic Statistics for Teachers Workshop at PIDE (Conducted 2 Sessions on
 +    Data Visualization and Exploration August, 2016) 
 +    MS Excel-Advanced Young Professional Induction Program Batch 5, NIBAF, State Bank 
	of Pakistan (20-22 June, 2016) 
 +    Visualization and Exploration of Data Using R for PIDE research staff and students
	(8-9 May, 2016).
	*Business Intelligence through Financial Modeling-Scenario-Building* for Senior
 +    Middle Management of SBP-BSC, NIBAF, Islamabad (4 hours), 2016 (2nd Iteration).
	*Business Intelligence through Financial Modeling-Scenario-Building* for Senior
 +    Middle Management of SBP-BSC, NIBAF, Islamabad (4 hours), 2016 
	
 +    *Use of Statistical Package for Social Sciences (SPSS) In Agricultural Statistics of Pakistan* Ministry of Food Security and Research, PARC, Islamabad Feb.24,2016 
	
 +    *MS Excel Advanced for SBP-BSC officers* at NIBAF Islamabad (Feb.22-23, 2016) 
	
 +    *Statistical Methods Using STATA* for Strengthening of Crops Estimation System in Pakistan by Capacity Building of the Officers.  Ministry of Food Security and
  Research, Islamabad, October 20,2015 
  
 +    *Applied Research Methods for Economics & Finance*, Department of Economics and
	Finance, PIDE, Islamabad September 7-11,2015 
	
 +    *Processing and Analysis of Data (Methodology and Software)* June10-12, 2015 
	*MS Office-Advanced (Excel, Word & PowerPoint) Young Professional Induction Program*. NIBAF, State Bank of Pakistan (22-25 April, 2015) 
	
 +    *Inflation, Measurement Issues and its Impact on Common Man* for Research Officers (Economist Group) M/O Planning, Development and Reform at PPMI, Islamabad (22 Oct, 2014) 
 +    *Data Analysis Using Excel-Advanced for Research Staff and Faculty*, Pakistan
	Institute of Development Economics, Islamabad (9-10 June, 2014)
 +    *Advanced Applied Econometrics Using STATA/ EVIEWS* for State Bank of Pakistan
 Officers at LRC, Karachi (24 June-5 July 2013)
 +    *Issues in Pakistan Economy*, State Bank Officers Training, NIBAF, 6th July, 2013 Islamabad
 +    *Advanced Econometrics Using STATA and EVIEWS* for State Bank of Pakistan Officers (Research, Statistics and Data Ware House wing) at LRC, Karachi (Feb-Mar 2013)
 +    *Applied Econometrics* for State Bank of Pakistan officers (Monetary and Economic Policy Division) at LRC, Karachi (2012)
 +    *Managerial Economics: International Business Administration & IT Course for Central Asian Republics* NIBAF, State Bank of Pakistan, (2012)
 +    *National Accounts*, State Bank Officers Training Scheme (2012)
	*Biostatistics and Genetic Epidemiology*, Quaid-i-Azam University, Islamabad. Served as Focal Person from Aug 02-11 (2016).
 +    *Two weeks training course on Statistics*, Planning Commission of Pakistan, Pakistan (2005)
 +    *Resource Person for Higher Education Commission Faculty Development Program* 2017 to-date
 	
## PhD thesis 

  Supervised: 5 
  
  Under-progress: 3

  Mphil thesis (Supervised): 40 + 

## References: 

  Upon request

    